LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-03-01 src/ms.tex
move eq.44 into averaging section

In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal and thus $\langle F_+ F_{\times}\rangle = 0$. This means we can rewrite Eq.~\ref{eq:signal} as 
\begin{equation}{}
    \begin{split}
        |\tilde{s}(f)|^2 &= |F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta)|^2\\
        &+ |F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
    \end{split}
\end{equation} 
which can then be applied to Eq.~\ref{eq:snr_general_start} as
\begin{equation}{}
\label{eq:snr_general_simpler}
    \rho^2 = 4 \int_0^{\infty} \frac{|F_+\tilde{h}_+|^2 + |F_{\times}\tilde{h}_{\times}|^2}{P_{\rm n}(f)} df.
\end{equation}

\subsubsection{Average over position and polarisation}
Now, we can consider averaging over different quantities. In particular, we can average over the sky position and polarisation as

\begin{equation}{}
\label{eq:position_orientation_ave}
    \langle \rho \rangle^2_{\theta,\phi,\psi} = 4 \int_0^{\infty} df \int \frac{d\Omega_{\theta,\phi}}{4\pi} \int \frac{d\psi}{\pi} \frac{|F_+\,\tilde{h}_+|^2 + |F_{\times}\,\tilde{h}_{\times}|^2}{P_{\rm n}(f)}.
\end{equation}
From \cite{Robson+2019}, we can write the position and polarisation average of the signal response function of the instrument, $\mathcal{R}$, as

>>>>

\subsubsection{Average over position and polarisation}
\referee{Now, we can consider averaging over different quantities. In LISA's case, when averaged over all angles and polarisations, the antenna patterns are orthogonal and thus $\langle F_+ F_{\times}\rangle = 0$. This means we can rewrite Eq.~\ref{eq:signal} as 
\begin{equation}{}
    \begin{split}
        |\tilde{s}(f)|^2 &= |F_+(\theta, \phi, \psi)\tilde{h}_+(\referee{f}, D_L, \iota, \beta)|^2\\
        &+ |F_{\times}(\theta, \phi, \psi)\tilde{h}_{\times}(\referee{f}, D_L, \iota, \beta)|^2,
    \end{split}
\end{equation}
which can then be applied to Eq.~\ref{eq:snr_general_start} to give
\begin{equation}{}
\label{eq:position_orientation_ave}
    \langle \rho \rangle^2_{\theta,\phi,\psi} = 4 \int_0^{\infty} df \int \frac{d\Omega_{\theta,\phi}}{4\pi} \int \frac{d\psi}{\pi} \frac{|F_+\,\tilde{h}_+|^2 + |F_{\times}\,\tilde{h}_{\times}|^2}{P_{\rm n}(f)}.
\end{equation}}
From \cite{Robson+2019}, we can write the position and polarisation average of the signal response function of the instrument, $\mathcal{R}$, as
